The importance of transient resonances in extreme-mass-ratio inspirals (new title?)

### 2015-06-08 res_char.tex
Overlap/order

We wish to test whether there exists some set of parameters $\Theta^a$ such that the resulting adiabatic waveform is sufficiently similar to the full waveform. We do this by evaluating the signal-to-noise ratio (SNR) for each waveform template, defined by
\begin{equation}
\rho\left[h\right] = \frac{\overlap{s}{h}}{\sqrt{\overlap{h}{h}}}.
\end{equation}
If a template were to exactly match the data, it would produce an SNR of $\sqrt{\overlap{s}{s}}$ and so the overlap
\begin{equation}
\label{eq:overlap}
\mathcal{O}\left[h\right] = \frac{\overlap{s}{h}}{\sqrt{\overlap{s}{s}}\sqrt{\overlap{h}{h}}}
\end{equation}
provides an indication of how well-matched the template is to the data. We leave an investigation into parameter estimation biases (where the parameters of the best-matching adiabatic $\Theta^a$ do not agree with the parameters of the system $\bar{\Theta}^a$) to future work.

@@

Once the trajectories have been computed using both methods of evolution, we can calculate the corresponding waveforms. The plus-polarised GW at the start and end of the evolution is shown in \figref{good-waveform}. The adiabatic waveform shows good agreement with the full waveform in both amplitude and phase. Calculating the SNR for each of the models, we find an overlap $\mathcal{O} = 0.984$, illustrating that adiabatic models can be used in place of the full evolution in cases where resonances are not encountered.

@@

None of the adiabatic models presented here give a particularly high overlap with the full evolution, because of the effects of the resonance. The best-performing adiabatic model was that which matched at the end, giving $\mathcal{O} = 0.677$, while the model that matches at the start gives only $\mathcal{O} = 0.202$. These values can be explained qualitatively by the relative lengths of the adiabatic-like regions on either side of the resonance in the full evolution.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[width=\textwidth]{Fig_EMRIpar_dists}
\caption{\label{fig:EMRIpar-dists}The parameter distributions for our detectable EMRI systems, generated using $\mathcal{O}(10^4)$ realisations. The (darker) blue bars represent the final distribution, including an SNR cut of 10. The (lighter) pink bars stacked on top indicate the full distribution before the SNR cut.}
\end{figure*}

>>>>

We wish to test whether there exists some set of parameters $\Theta^a$ such that the resulting adiabatic waveform is sufficiently similar to the full waveform. We do this by evaluating the signal-to-noise ratio (SNR) for each waveform template, defined by
\begin{equation}
\rho\left[h\right] = \frac{\overlap{s}{h}}{\sqrt{\overlap{h}{h}}}.
\end{equation}
If a template were to exactly match the data, it would produce an SNR of $\sqrt{\overlap{s}{s}}$ and so the overlap
\begin{equation}
\label{eq:overlap}
\mathbb{O}\left[h\right] = \frac{\overlap{s}{h}}{\sqrt{\overlap{s}{s}}\sqrt{\overlap{h}{h}}}
\end{equation}
provides an indication of how well-matched the template is to the data. We leave an investigation into parameter estimation biases (where the parameters of the best-matching adiabatic $\Theta^a$ do not agree with the parameters of the system $\bar{\Theta}^a$) to future work.

@@

Once the trajectories have been computed using both methods of evolution, we can calculate the corresponding waveforms. The plus-polarised GW at the start and end of the evolution is shown in \figref{good-waveform}. The adiabatic waveform shows good agreement with the full waveform in both amplitude and phase. Calculating the SNR for each of the models, we find an overlap $\mathbb{O} = 0.984$, illustrating that adiabatic models can be used in place of the full evolution in cases where resonances are not encountered.

@@

None of the adiabatic models presented here give a particularly high overlap with the full evolution, because of the effects of the resonance. The best-performing adiabatic model was that which matched at the end, giving $\mathbb{O} = 0.677$, while the model that matches at the start gives only $\mathbb{O} = 0.202$. These values can be explained qualitatively by the relative lengths of the adiabatic-like regions on either side of the resonance in the full evolution.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[width=\textwidth]{Fig_EMRIpar_dists}
\caption{\label{fig:EMRIpar-dists}The parameter distributions for our detectable EMRI systems, generated using $\order{10^4}$ realisations. The (darker) blue bars represent the final distribution, including an SNR cut of 10. The (lighter) pink bars stacked on top indicate the full distribution before the SNR cut.}
\end{figure*}
